Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-03 paper/paper.tex
added draft acknowledgments

\subsection{Computational analysis of single-cell transcriptomic and viral sequence data}
A computational pipeline that performs all steps in the data analysis is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell}~\citep{russell2018github}. 
This pipeline is orchestrated by \texttt{Snakemake}~\citep{koster2012snakemake}, and begins with the raw sequencing data and ends by generating the figures shown in this paper.
The sequencing data and annotated cell-gene matrix are available on the GEO repository under \jdbcomment{add accession}.

@@

\section{Acknowledgments}
Andy Marty and Genomics Core.
Cole Trapnell.
Jason Underwood.
AJ Velthuis. 
\jdbcomment{Finish this}

>>>>

\subsection{Computational analysis of single-cell transcriptomic and viral sequence data}
A computational pipeline that performs all steps in the data analysis is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell}~\citep{russell2018github}. 
This pipeline is orchestrated by \texttt{Snakemake}~\citep{koster2012snakemake}, and begins with the raw sequencing data and ends by generating the figures shown in this paper.
The sequencing data and annotated cell-gene matrix are available on the GEO repository under \jdbcomment{data have been uploaded to GEO, but accession not yet available. The accession number will be added to the README of the GitHub repo at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell} as soon as it's available}.

@@

\section{Acknowledgments}
We thank Cole Trapnell, Jason Underwood, Robert Bradley, Daniel Stetson, and AJ Velthuis for helpful scientific suggestions.
We thank Andy Marty and the Fred Hutch Genomics Core for performing the deep sequencing.
We thank Katherine Xue, David Bacsik, and Hannah Itell for comments on the manuscript.
This work was supported by the NIAID of the NIH under grant R01 AI127893 and a Burroughs Wellcome Fund Young Investigator in the Pathogenesis of Infectious Diseases grant to JDB.
ABR was supported by a postdoctoral fellowship from the Damon Runyon Cancer Research Foundation.
JDB is an Investigator of the Howard Hughes Medical Institute.
The funders had no role in study design, data collection and interpretation, or the decision to submit the work for publication.
The authors declare that no competing interests exist.
